A free/open-source Kazakh-Tatar machine translation system

### 2013-04-06 paper/paper.tex
a little poking

\documentclass[11pt,a4paper]{article}
\usepackage{mtsxiv}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
\usepackage{times}
\usepackage{multirow}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

Both languages belong to the Kypchak (or Northwestern) group of Turkic
languages. Kazakh is primarily spoken in Kazakhstan, where it is the national
language. Large groups of native speakers also exist in China, neigbouring
Central-Eurasian republics and Mongolia. Total number of speakers is at least
10 million people. Tatar is a Turkic language spoken in and around Tatarstan by
approximately 6 million people. It is co-official with Russian in Tatarstan --
a republic within Russia.

@@

Several previous works on making machine translation systems between
Turkic languages exist, although to our knowledge none are publically available.
For systems between Turkish and other Turkic languages, there have been,
for example, systems reported for Turkish-Crimean Tatar \citep{altintas01},
Turkish-Azerbaijani \citep{hamzaoglu93}, Turkish-Tatar \citep{suleymanov08}, and
Turkish-Turkmen \citep{tantug07}.

A prototype Tatar-Bashkir machine translation system was built by ourselves.
Due to the closeness of the languages, it proved to provide high accuracy
translations, but being a prototype system by design, had relatively low
coverage.

@@

\bibliographystyle{lrec2012}
\bibliography{tt-ba}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{mtsxiv}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
%\usepackage{times}
\usepackage{multirow}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

Both Tatar and Kazakh belong to the Kypchak (or Northwestern) group of Turkic
languages. Kazakh is primarily spoken in Kazakhstan, where it is the national
language. Large groups of native speakers also exist in China, neigbouring
Central-Eurasian republics, and Mongolia. The total number of speakers is at least
10 million people. Tatar is a Turkic language spoken in and around Tatarstan by
approximately 6 million people. It is co-official with Russian in Tatarstan --
a republic within Russia.  A majority of native speakers of both languages are bilingual in Russian.

@@

Several previous works on making machine translation systems between
Turkic languages exist, although to our knowledge none are publically available.
%FIXME: tr-az, tr-ky
For systems between Turkish and other Turkic languages, there have been systems reported for Turkish-Crimean Tatar \citep{altintas01},
Turkish-Azerbaijani \citep{hamzaoglu93}, Turkish-Tatar \citep{suleymanov08}, and
Turkish-Turkmen \citep{tantug07}, though none of these have been released to a public audience.

A prototype Tatar-Bashkir machine translation system was built by the authors of this paper \citep{tyerswashingtonsalimzyanbattalov12}.
Due to the closeness of the languages, it proved to provide high accuracy
translations, but being a prototype system by design, had relatively low
coverage.

@@

%\bibliographystyle{lrec2012}
%\bibliography{tt-ba}
\bibliographystyle{apa}
\bibliography{paper}
